Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-07-11 intro.tex
Modificaciones en intro related y techniques

In this work, we compare five machine learning techniques to predict
the development rate of the black Sigatoka disease: support vector
regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression,
using input variables such as: air temperature, relative humidity, solar radiation, precipitation and wind speed \review{completar las variables de
  entrada usada - Modificado} to predict the evolution stage in the biological warning system\review{completar las variables de salida - Modificado}.

>>>>

In this work, we compare five machine learning techniques to predict
the development rate of the black Sigatoka disease: support vector
regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression,
using input variables such as: air temperature, relative humidity, solar radiation, precipitation and wind speed \review{LISTO - completar las variables de
  entrada usada} to predict the evolution stage in the biological warning system\review{LISTO - completar las variables de salida - Modificado}.

### 2016-07-11 techniques.tex
Typos fixed
Modificaciones en intro related y techniques

  Comentario:  Pero si por feature scaling los datos están entre -1 y 1, con 0 en medio?}

@@

  Comentario: En realidad la idea era mostrar los diversos resultados, pero me suena bien reducirlo a ElasticNet (optimizado los parámetros) lo cual reduce resultados y gráficos en dos (quitando ridge y OLSR).  Cuando hablamos confirmamos y lo quito.  }

@@

\TODO{Estoy seguro que los lectores van a solicitar reducir esto y
  dejar solo la referencia.  Dejé solo lo que considero relevante,
  pero podés reducirlo más, si querés.}

From the perspective of Support Vector Regression (SVR) the regression
function is usually formulated as 
\begin{equation}
\label{eq:svrfunc}
  \tilde{y} = f(\vct{x}) = \dotp{\vct{w},\vct{x}} + b
\end{equation}
The weights are selected in a convex optimization problem
\citep{Smola2004}:
\begin{align*}
  \text{minimize}   & \frac{1}{2}\|\vct{w}\|^2 + C\sum_{i=1}^n(\xi_i+\xi_i^\ast \\
  \text{subject to} & 
  \begin{cases}
    y_i - \dotp{\vct{w},\vct{x}_i} - b &\leq \epsilon + \xi_i    \\
    \dotp{\vct{w},\vct{x}_i} + b -y_i  &\leq \epsilon + \xi_i^\ast\\
    \xi_i,\xi_i^\ast               &\geq 0
  \end{cases}
\end{align*}
where $\epsilon$ is the maximal allowed deviation of the targets
$\tilde{y}_i$ from the responses $y_i$, the slack variables $\xi_i$
and $\xi_i^\ast$ allow to cope with otherwise unfeasible constraints
for the optimization problem, and the constant $C>0$ controls the
trade-off between the flatness of $f$ and the tolerance to deviations
larger than $\epsilon$.

@@

RBF: 
\begin{equation*}
K(\vct{x}_i,\vct{x}_j)= exp{\vct{x}_i}^T \vct{x}_j
\end{equation*}

%K(x_i,x_j )=  exp((||x_i- x_j | |^2)/(2σ^2 ))
%donde σ es el parámetro del modelo Gausiano.

Sigmoid:
%K(x_i,x_j )=  tanh[-c+ (x_i x_j)/σ^2 ]
%Con c ≥0  y σ^2 es el vector de escalamiento

\TODO{Habría que insertar aquí los kernels utilizados en los experimentos}

@@

For a given training input signal $u(n) \in \setR^{N_u}$ a desired target
output signal $y^{target}(n) \in \setR^{N_y}$ is known.
%
Here $n = 1,\ldots,T$ is the discrete time and \todofn{$T$ is the number of
data points in the training dataset.}{No puede ser!}

>>>>

  COMENTARIO:  Modificado según lo conversado}

@@

  Comentario: Revisando la documentación de la bibliteca (ver abajo), parece que por implementación no debería excluirse OLSR por separado.
  Estos son dos parámetros de las ElasticNet
alpha : float.  Constant that multiplies the penalty terms. Defaults to 1.0 See the notes for the exact mathematical meaning of this parameter. alpha = 0 is equivalent to an ordinary least square, solved by the LinearRegression object. For numerical reasons, using alpha = 0 with the Lasso object is not advised and you should prefer the LinearRegression object.
l1ratio    The ElasticNet mixing parameter, with 0 < = l1ratio < = 1. For l1ratio = 0 the penalty is an L2 penalty. For l1ratio = 1 it is an L1 penalty. For 0 < l1ratio < 1, the penalty is a combination of L1 and L2 }

@@

\TODO{Estoy seguro que los lectores van a solicitar reducir esto y
  dejar solo la referencia.  Dejé solo lo que considero relevante,
  pero podés reducirlo más, si querés.

  Comentario: Ok, gracias }

From the perspective of Support Vector Regression (SVR) the regression
function is usually formulated as 
\begin{equation}
\label{eq:svrfunc}
  \tilde{y} = f(\vct{x}) = \dotp{\vct{w},\vct{x}} + b
\end{equation}
The weights are selected in a convex optimization problem
\citep{Smola2004}:
\begin{align*}
  \text{minimize} \quad  & \frac{1}{2}\|\vct{w}\|^2 + C\sum_{i=1}^n(\xi_i+\xi_i^\ast) \\
  \text{subject to} \quad & 
  \begin{cases}
    y_i - \dotp{\vct{w},\vct{x}_i} - b &\leq \epsilon + \xi_i    \\
    \dotp{\vct{w},\vct{x}_i} + b -y_i  &\leq \epsilon + \xi_i^\ast\\
    \xi_i,\xi_i^\ast               &\geq 0
  \end{cases}
\end{align*}
where $\epsilon$ is the maximal allowed deviation of the targets
$\tilde{y}_i$ from the responses $y_i$, the slack variables $\xi_i$
and $\xi_i^\ast$ allow to cope with otherwise unfeasible constraints
for the optimization problem, and the constant $C>0$ controls the
trade-off between the flatness of $f$ and the tolerance to deviations
larger than $\epsilon$.

@@

Radial basis function (RBF): 
\begin{equation*}
K(\vct{x}_i,\vct{x}_j) = exp\left( \frac{ \| \vct{x}_i - \vct{x}_j \|^2}{2 \sigma^2} \right)
\end{equation*}
where $\sigma$ is the parameter of gausian model.

Sigmoid:
\begin{equation*}
K(\vct{x}_i,\vct{x}_j) = tanh \left[ -c + \frac{ \vct{x}_i  \vct{x}_j }{ \sigma^2} \right]
\end{equation*}
with $c \geq 0$  and $\sigma^2$ is the scaling vector.

\TODO{LISTO - Habría que insertar aquí los kernels utilizados en los experimentos}

@@

For a given training input signal $u(n) \in \setR^{N_u}$ a desired target
output signal $y^{target}(n) \in \setR^{N_y}$ is known.
%
Here $n = 1,\ldots,T$ is the discrete time and \todofn{$T$ is the number of
data points in the training dataset.}{No puede ser! -- Así está en el paper original, lo puse en el repositorio}
